---
title: "App Usage v.s. Time"
author: "Geoffrey Wong"
date: "2025-07-28"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(coefplot)
library(lmtest)
```

# App Usage v.s. Time

## Data Loading

```{r}
# Set the file path to your CSV file
file_path <- "app_usage_app_info.csv"

# Read the CSV file
data <- read.csv(file_path)

# Define the breaks for different time ranges
breaks <- c(-Inf, 6, 12, 18, 24)

# Labels for the time ranges
labels <- c("0-5", "6-11", "12-17", "18-23")

# Convert hours column to categorical variable representing different time ranges
data$hour_range <- cut(data$hour_of_day, breaks = breaks, labels = labels, include.lowest = TRUE)

# Print the first few rows of the data
head(data)
```
## Transformation

```{r}
# Convert day_of_week, is_weekend, and hour_of_day to factors for correct grouping
data$day_of_week <- as.factor(data$day_of_week)
data$is_weekend <- as.factor(data$is_weekend)
data$hour_range <- as.factor(data$hour_range)

# Group by the specified columns and sum the foreground_time_ms
result <- data %>%
  group_by(applicationCategory, is_weekend, hour_range) %>%
  summarise(n_user_id = n_distinct(user_id))

# Print the resulting data frame
head(result)
```
## Full Model
```{r}
# Perform linear regression analysis
full_model <- lm(n_user_id ~  applicationCategory + is_weekend + hour_range, data = result)
# Summarize the linear regression model
summary(full_model)
```
```{r}
coefplot(full_model)
```
## Interaction Model

```{r}
# Perform linear regression analysis
inter_model <- lm(n_user_id ~  (applicationCategory + is_weekend + hour_range)^2, data = result)
# Summarize the linear regression model
summary(inter_model)
```

***RESULT:*** The cardinality of the interaction model is too high to be interpretted, but at least we can still say there are more user (on an hourly basis) during weekday than weekend, and this is mostly because there is much lower phone usage in the morning (6am to 11am).

## Asssumption Testing for Interaction Model

```{r}
plot(inter_model, which = 1)
```
```{r}
dwtest(inter_model)
```

```{r}
plot(inter_model, which = 3)
```

```{r}
qqnorm(resid(inter_model))
qqline(resid(inter_model))
```

***RESULT:*** The interaction models passes the Linearity, Independence, Homoscedasticity, and Normality Assumption.